\section{Interim Milestones}\label{Interim_milestones}

% Beschrijf in dit hoofdstuk welke producten je oplevert waar je met de uitvoering van de activiteiten naar
% toewerkt. Deze producten leiden dan samen naar het eindproduct. Voorbeelden van producten zijn:
% - Een verslag;
% - Tijdsplanning;
% - Een ontwerp
% - Een meetrapport
% - Een tekening;
% - Etc.

During the \textbf{PROJE4} course \textbf{Alset Innovations} will be designing a motor driver to drive a 78 Watts motor continuously. To achieve this a set of deliverables must be completed and delivered. These deliverables are mainly Reports and documents about the progress of the project. A detailed list is provided below.

\begin{itemize}
    \item Plan of Approach
        \begin{itemize}
            \item A detailed report about the Plan of Approach of \textbf{Alset Innovations}.
        \end{itemize}
    \item Intermediate Assessment 1
        \begin{itemize}
            \item Document in PDF format listing all of the detailed design requirements
            in relation to the software, including both interface and functionality
            requirements.
            \item Well documented and formatted code in original an pdf file formats.
            \item Summary of completed tests including hardware and software tests.
        \end{itemize}
    \item Intermediate Assessment 2
        \begin{itemize}
            \item Document in PDF format all of the detailed design requirements.
            in relation to the hardware.
            \item A zip file containing all PCB related design files as well as data-sheets for all active components.
            \item A well formatted pdf file containing pages showing both the schematic
            and the layout for the PCB design. The layout should be in a clear
            format such that it can be easily reviewed both from the top level
            design perspective and the individual layers.
            \item Maximum two page summary of the progress of the project, including
            the results of any tests on actual prototype hardware.
        \end{itemize}
    \item Final Assessment
        \begin{itemize}
            \item A detailed final report according to the provided template. In addition each student is required to write about their competencies.
        \end{itemize}
\end{itemize}